\LARGE \bf Eye-Tracking: a New Look at Human-Robot Interaction Assessment

### 2014-10-02 paper.tex
Article overview

The prime advantage of using mobile eye-tracking is that the users' interaction
with the robot can still be ecologically valid. On the other hand, using fMRI
for evaluating HRI reduces the interaction to a video of the robot only
~\cite{rosenthal2013neural}.

@@

\paragraph{Article overview}
\fixme{write it}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Eye Tracking as a Tool for Assessing Social Interaction}

@@

\section{State of Eye Tracking in Human-Robot Interaction}

@@

\section{Method description}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Eye-tracking}

@@

\section{Method Application Example}
In this section, we present a mobile eye-tracking study with an educational robot Thymio II. The study exemplifies one of the use cases of the mobile eye-tracking. One part of the target (the robot) was moving, whereas the rest of the maze (or playground, figure~\ref{playground}, as we refer to it in the rest of this paper) was stationary. The participants were allowed to move but most of them remained seated for the duration of the experiment. For the purpose of the eye-tracking data analysis, we used the proportions of fixations on different  area of interest on the playground.

@@

\section{Interpreting the results}

@@

\section{Conclusion}

>>>>

The prime advantage of using mobile eye-tracking is that the users' interaction
with the robot can still be ecologically valid. On the other hand, using fMRI
for evaluating HRI reduces the interaction to a video of the robot
only~\cite{rosenthal2013neural}.

@@

\paragraph{Article overview}

The article is structured as follow: section~\ref{et_assessing} presents the
main lines of research in eye-tracking-based assessment of cognitive
tasks and interaction. It evidences the breadth of the field, both on individual
and social tasks. Section~\ref{et_robotics} contrasts this literature with the
current state-of-the-art of eye-tracking in HRI. We distinguish here two main
applications: eye-tracking as an \emph{interaction modality} and eye-tracking as
an \emph{interaction assessment} tool. It appears that the literature in both
these fields is scarce.

Section~\ref{method} presents in a brief yet exhaustive way eye-tracking as an
investigation method: we introduce the main eye-tracking techniques (including
mobile eye-tracking and dual eye-tracking) and discuss their respective domains
of application. We then present five important techniques for eye-tracking data
analysis and emphasise the analysis techniques that are the most relevant to the
study of social interaction.

Next, section~\ref{application} presents a case study with 52 subjects
interacting with a robot. The study acts both as a demonstration of the
integration of eye-tracking in HRI studies, and as an example of a possible
eye-tracking setup. Then, section~\ref{interpretation} goes over the analysis of
the study data and its interpretation, and illustrates this process.

We conclude the article with a summary of the strengths of eye-tracking to
analyse the complex socio-cognitive situations that characterise human-robot
interaction, as well as a few notes on the limitations of this method.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Eye Tracking as a Tool for Assessing Social Interaction}
\label{et_assessing}

@@

\section{State of Eye Tracking in Human-Robot Interaction}
\label{et_robotics}

@@

\section{Method description}
\label{method}

\subsection{Eye-tracking}

@@

\section{Method Application Example}
\label{application}

In this section, we present a mobile eye-tracking study with an educational robot Thymio II. The study exemplifies one of the use cases of the mobile eye-tracking. One part of the target (the robot) was moving, whereas the rest of the maze (or playground, figure~\ref{playground}, as we refer to it in the rest of this paper) was stationary. The participants were allowed to move but most of them remained seated for the duration of the experiment. For the purpose of the eye-tracking data analysis, we used the proportions of fixations on different  area of interest on the playground.

@@

\section{Interpreting the results}
\label{interpretation}

@@

\section{Conclusion}
\label{conclusion}
